First round comments from the Ad-hoc rewiew committee \\ (Maurik Holtrop, Kevin Giovankl, Zein-Eddine Meziani)

### 2018-09-06 eg6-letters/incoherent/adhocreview/1st_adhoc_comments.tex
some cleaning

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{blue}{The text is updated. We show the dependence on $t$ as it 
      is mostly related to the modifications of the GPDs.}

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure6.\\
   \textcolor{blue}{For this specific purpose, we applied four dimensional 
      binning to our incoherent DVCS data to get kinematical mean values close 
      to the published free proton results. The review committee members are 
      invited to check Appendix J in the analysis note. }

@@

\item    Line 206: To make it more clear to the reader what you are doing with 
   the data, you should explicitly state that you make a fit of the $\phi$ 
      distributions, and then extract the $a_0$ value as $A_{LU}$(90). You 
      should also explicitly state that when plotting versus one kinematic 
      variable, you integrate over all the other kinematic variables. This 
      relates to comment \#2 above.\\
      \textcolor{red}{Cleaned. ( I am not sure this is needed as it is 
      mentioned at the beginning of the paragraph).}

>>>>

\item    For figure 6, you state that "our experiment shows a sharp drop" (line 
   250), in the incoherent $A_{LU}$/proton $A_{LU}$. You do indeed have a 
      single point, at the lowest $x_B$, that is lower than the other three, 
      but it seems that I can draw a straight horizontal line through all 4 
      error bars. It seems too strong a statement to speak of a sharp drop 
      here, and subsequently conclude that there is "strong quenching of the 
      BSA" (line 253). If I contrast this graph with figure 5, where you state 
      that "$A_{LU}$ does not indicate a strong dependence on $Q^2$", I agree 
      with you. The variation between the point in figure 5 is however similar 
      to that in figure 6, except the order of the variation is different.\\ 
      \textcolor{blue}{We replaced the figure with the t-dependence, and 
      changed the wording in the text accordingly. We believe t-dependence 
      better reflects difference between the free and bound nucleon structures, 
      and shows clear difference with existing theoretical models.}

\item    To further consider this statement, I looked up ref. 21, which 
   contains the proton data that you divide by. This data is not, however, 
      shown as a function of $x_B$, but in a set of tiles, with variation in -t 
      shown for different $x_B$ and $Q^2$ average values. It is then not quite 
      clear how you used this data to get the data points to divide out the 
      proton $A_{LU}$. How closely do the kinematics agree? How does this 
      procedure affect the systematic uncertainties? This is important 
      information to make a judgement on the validity of your figure~6.\\
   \textcolor{blue}{The ratio of $A_{LU}$s were derived in two ways, in the  
      first method we studied and parameterized $x_B$, $Q^2$, and t-dependences 
      of free proton $A_{LU}$ from ref~[21]. Then using this parametrizations 
      we calculated $A_{LU}$s for free proton at kinematic points of our data.  
      In the second method we selected events in our analysis such that 
      kinematics of selected events matched kinematics of the free proton 
      points for the t-dependence of the ratio. In the figure we use results of 
      the first method since statistics is higher for our data. The difference 
      in ratios calculated with these two methods was taken as systematic error 
      for the ratio. The details can be found in the analysis note (appendix 
      J).  }

@@

\item    Line 206: To make it more clear to the reader what you are doing with 
   the data, you should explicitly state that you make a fit of the $\phi$ 
      distributions, and then extract the $a_0$ value as $A_{LU}$(90). You 
      should also explicitly state that when plotting versus one kinematic 
      variable, you integrate over all the other kinematic variables. This 
      relates to comment \#2 above.\\
      \textcolor{blue}{Cleaned. }
